%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

	%---------------------------------------------------------
	\cventry
	{Bachelor's Degree in Computer Science} % Degree
	{Università degli Studi di Napoli "Parthenope"} % Institution
	{Naples, Italy} % Location
	{Sep. 2022 - Expected Nov. 2026} % Date(s)
	{
		\begin{cvitems} % Description(s) bullet points
			\item {Solid foundation in applying mathematical and logical principles to problem-solving, coupled with proficiency in Computer Science methodologies.}
			\item {Through hands-on experiences like labs, projects, and internships, I've mastered algorithm design, software development, data management, and artificial intelligence.}
			\item {My skills extend to web and mobile applications, distributed systems, and creating effective communication interfaces.}
		\end{cvitems}
	}

	\cventry
	{High School Diploma in Computer Science} % Degree
	{I.T.I.S. G. Ferraris} % Institution
	{Naples, Italy} % Location
	{Sep. 2016 - Jul. 2021} % Date(s)
	{
		\begin{cvitems} % Description(s) bullet points
			\item {Focused on a comprehensive Computer Science curriculum, covering software engineering, database management, and network infrastructure.}
			\item {Developed foundational skills in programming languages such as C, C++, and Java, with an emphasis on logic and structured programming.}
			\item {Participated in technical labs and projects involving system administration, telecommunications protocols, and web development basics.}
		\end{cvitems}
	}

	%---------------------------------------------------------
\end{cventries}
